The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2010-03-25 script/de/chapters/authors.tex
Minor grammar corrections in German and English script.

\paragraph{Anmerkung 2:}
Abgebildet und beschrieben finden Sie einige dieser Buchtitelseiten
auf der Webseite von Tobias Schrödel, der sich vor allem mit antiken
Büchern zur Kryptographie beschäftigt: 
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}  % hier kein \\ ans Ende, sonst Warnung. Und in neuer Zeile wirkungslos, deshalb vspace.
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

@@

\vskip +20 pt
\paragraph{Anmerkung 1:}
Abgebildet und beschrieben finden Sie viele dieser Kinderbuch-Titelseiten
auf der Webseite von Tobias Schrödel, der sich vor allem mit antiken
Büchern zur Kryptographie beschäftigt:
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

>>>>

\paragraph{Anmerkung 2:}
Abgebildet und beschrieben finden Sie einige dieser Buchtitelseiten
auf der Webseite von Tobias Schrödel\index{Schrödel, Tobias}, der sich vor allem mit
antiken Büchern zur Kryptographie beschäftigt: 
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}  % hier kein \\ ans Ende, sonst Warnung. Und in neuer Zeile wirkungslos, deshalb vspace.
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

@@

\vskip +20 pt
\paragraph{Anmerkung 1:}
Abgebildet und beschrieben finden Sie viele dieser Kinderbuch-Titelseiten
auf der Webseite von Tobias Schrödel\index{Schrödel, Tobias}, der sich vor allem mit
antiken Büchern zur Kryptographie beschäftigt:
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

### 2010-03-25 script/de/chapters/digitalsignatures.tex
Minor grammar corrections in German and English script.

Kryptographisch sichere Hashfunktionen erfüllen folgende drei Anforderungen
(Reihenfolge so, dass die Anforderungen ansteigen):
\begin{itemize}
 \item Standhaftigkeit gegen 1st-Pre-Image-Attacks:
      \index{Pre-Image-Attack!1st} \index{Angriff!Pre-Image-Attack!1st}  \\
      Es sollte praktisch unmöglich sein, zu einer gegebenen Zahl eine
      Nachricht zu finden, die genau diese Zahl als Hashwert hat. \\
      Gegeben (fix): Hashwert H', \\
      Gesucht: Nachricht m, so dass gilt: H(m) = H'.
 \item Standhaftigkeit gegen 2nd-Pre-Image-Attacks:
      \index{Pre-Image-Attack!2nd} \index{Angriff!Pre-Image-Attack!2nd}  \\
      Es sollte praktisch unmöglich sein, zu einer gegebenen Nachricht
      eine zweite Nachricht zu finden, die genau denselben Hashwert hat. \\
      Gegeben (fix): Nachricht m1 [und damit der Hashwert H1 = H(m1)], \\
      Gesucht: Nachricht m2, so dass gilt: H(m2) = H1.
 \item Standhaftigkeit gegen Kollisionsangriffe:
      \index{Angriff!Kollisionsangriff}  \\
      Es sollte es praktisch unmöglich sein, zwei (beliebige) Nachrichten
      mit demselben Hashwert (welcher ist egal) zu finden. \\
      Gesucht: 2 Nachrichten m1 und m2, so dass gilt: H(m1) = H(m2).
\end{itemize}

>>>>

Kryptographisch sichere Hashfunktionen erfüllen folgende drei Anforderungen
(Reihenfolge so, dass die Anforderungen ansteigen):
\begin{itemize}
 \item Standhaftigkeit gegen 1st-Pre-Image-Attacks:
      \index{Pre-Image-Attack!1st} \index{Angriff!Pre-Image!1st}  \\
      Es sollte praktisch unmöglich sein, zu einer gegebenen Zahl eine
      Nachricht zu finden, die genau diese Zahl als Hashwert hat. \\
      Gegeben (fix): Hashwert H', \\
      Gesucht: Nachricht m, so dass gilt: H(m) = H'.
 \item Standhaftigkeit gegen 2nd-Pre-Image-Attacks:
      \index{Pre-Image-Attack!2nd} \index{Angriff!Pre-Image!2nd}  \\
      Es sollte praktisch unmöglich sein, zu einer gegebenen Nachricht
      eine zweite Nachricht zu finden, die genau denselben Hashwert hat. \\
      Gegeben (fix): Nachricht m1 [und damit der Hashwert H1 = H(m1)], \\
      Gesucht: Nachricht m2, so dass gilt: H(m2) = H1.
 \item Standhaftigkeit gegen Kollisionsangriffe:
      \index{Angriff!Kollisionsangriff}  \\
      Es sollte es praktisch unmöglich sein, zwei (beliebige) Nachrichten
      mit demselben Hashwert (welcher ist egal) zu finden. \\
      Gesucht: 2 Nachrichten m1 und m2, so dass gilt: H(m1) = H(m2).
\end{itemize}

### 2010-03-25 script/de/chapters/numbertheory.tex
Minor grammar corrections in German and English script.

\begin{itemize}
\item [\bf a)] 
      {\bf Logarithmieren\index{Logarithmieren} (Bestimmen von $c$) -- Diskretes
       Logarithmusproblem\index{Logarithmusproblem!diskret}:\footnotemark}
\footnotetext{%
Weitere Details zum \index{Logarithmusproblem!diskret}
\hyperlink{HT-Discrete-Logarithm-as-Basis}{Diskreten Logarithmusproblem}
finden sie in Kapitel~\ref{L-Discrete-Logarithm-as-Basis}.
}

@@

\begin{remark}{:}\\
In diesem Beispiel mit den kleinen Zahlen ist das Diskrete
Logarithmusproblem\index{Logarithmusproblem!diskret} leicht lösbar, aber mit großen
Zahlen ist es kaum zu lösen\footnote{%
Mit Sage\index{Sage} kann man den diskreten Logarithmus\index{Logarithmusproblem!diskret} $x$,
der die Gleichung $11^x \equiv 49 {\rm ~(mod~}347)$ löst, folgendermaßen bestimmen
                % $11^x \equiv 49 \pmod{347}$
(hier für Allice):
\texttt{discrete\_log(mod(49, 347), mod(11, 347))}. Als Ergebnis erhält man $67$.\\
Solche zahlentheoretischen Aufgaben können auch mit anderen Tools wie PariGP\index{Pari-GP},
LiDIA\index{LiDIA}, BC\index{BC} oder Mathematica\index{Mathematica}
(siehe Anhang Web-Links am Ende dieses Kapitel) gelöst werden:\\
können solche zahlentheoretischen Aufgaben gelöst werden.\\
- Pari-GP: \texttt{znlog(Mod(49,347),Mod(11,347))}.\\
- LiDIA:   \texttt{dl(11,49,347)}.\\
- Mathematica: Die allgemeine Funktion ``Solve'' liefert die {em tdep}-Meldung
  ``The equations appear to involve the variables to be solved for in an essentially
    non-algebraic way''.\\
- Mathematica\index{Mathematica}: {\tt MultiplicativeOrder[11, 347, 49]}.\\
Alle liefern das Ergebnis $67$.
}${}^,$\footnote{%
Warum haben die Funktionen für den diskreten Logarithmus\index{DL-Problem} für Alice
den Wert $67$ geliefert und nicht den Wert 240, den Alice als Exponent $a$ wählte?\\
Der diskrete Logarithmus ist der kleinste natürliche Exponent, der die
Gleichung $11^x \equiv 49{\rm ~(mod~}347)$ löst. Sowohl $x=67$ als auch $x=240$ (die im Beispiel
gewählte Zahl) erfüllen die Gleichung und können damit zur Berechnung des
Sessionkeys benutzt werden: $285^{240}  \equiv 285^{67} \equiv 268 {\rm ~(mod~}347)$.
Hätten Alice und Bob als Basis $g$ eine Primitivwurzel\index{Primitivwurzel} modulo $p$ gewählt,
dann gibt es für jeden Rest aus der Menge
$\{1, 2, \cdots, p-1\}$ genau einen Exponenten aus der Menge $\{0, 1, \cdots, p-2\}.$ \\
Info: Zum Modul $347$ gibt es $172$ verschiedene Primitivwurzeln, davon sind $32$
prim (ist nicht notwendig).
Da die im Beispiel für $g$ gewählte Zahl $11$ keine Primitivwurzel\index{Primitivwurzel}
von $347$ ist, nehmen die Reste nicht alle Werte aus der Menge $\{1, 2, \cdots, 346\}$ an.
Somit kann es für einen bestimmten Rest mehr als einen oder auch gar keinen
Exponenten aus der Menge $\{0, 1, \cdots, 345\}$ geben, der die Gleichung
erfüllt. \\
Mit den entsprechenden Sage-Funktionen\index{Sage} findet man: \\
\texttt{is\_prime(347)=True}, \texttt{euler\_phi(347)=346}, \texttt{gcd(11,347)=1} und 
\texttt{multiplicative\_order(mod(11, 347))=173}.

>>>>

\begin{itemize}
\item [\bf a)] 
      {\bf Logarithmieren\index{Logarithmieren} (Bestimmen von $c$) -- Diskretes
       Logarithmusproblem\index{Logarithmusproblem!diskret}\index{DL-Problem}\index{Diskreter Logarithmus}:\footnotemark}
\footnotetext{%
Weitere Details zum \index{Logarithmusproblem!diskret}
\hyperlink{HT-Discrete-Logarithm-as-Basis}{Diskreten Logarithmusproblem}
finden sie in Kapitel~\ref{L-Discrete-Logarithm-as-Basis}.
}

@@

\begin{remark}{:}\\
In diesem Beispiel mit den kleinen Zahlen ist das Diskrete
Logarithmusproblem\index{Logarithmusproblem!diskret} leicht lösbar, aber mit großen
Zahlen ist es kaum zu lösen\footnote{%
Mit Sage\index{Sage} kann man den diskreten Logarithmus\index{Logarithmusproblem!diskret} $x$,
der die Gleichung $11^x \equiv 49 {\rm ~(mod~}347)$ löst, folgendermaßen bestimmen
                % $11^x \equiv 49 \pmod{347}$
(hier für Allice):
\texttt{discrete\_log(mod(49, 347), mod(11, 347))}. Als Ergebnis erhält man $67$.\\
Solche zahlentheoretischen Aufgaben können auch mit anderen Tools wie PariGP\index{Pari-GP},
LiDIA\index{LiDIA}, BC\index{BC} oder Mathematica\index{Mathematica}
(siehe Anhang Web-Links am Ende dieses Kapitel) gelöst werden:\\
können solche zahlentheoretischen Aufgaben gelöst werden.\\
- Pari-GP: \texttt{znlog(Mod(49,347),Mod(11,347))}.\\
- LiDIA:   \texttt{dl(11,49,347)}.\\
- Mathematica: Die allgemeine Funktion ``Solve'' liefert die {em tdep}-Meldung
  ``The equations appear to involve the variables to be solved for in an essentially
    non-algebraic way''.\\
- Mathematica\index{Mathematica}: {\tt MultiplicativeOrder[11, 347, 49]}.\\
Alle liefern das Ergebnis $67$.
}${}^,$\footnote{%
Warum haben die Funktionen für den diskreten
Logarithmus\index{DL-Problem}\index{Logarithmusproblem!diskret}\index{Diskreter Logarithmus} für Alice
den Wert $67$ geliefert und nicht den Wert 240, den Alice als Exponent $a$ wählte?\\
Der diskrete Logarithmus ist der kleinste natürliche Exponent, der die
Gleichung $11^x \equiv 49{\rm ~(mod~}347)$ löst. Sowohl $x=67$ als auch $x=240$ (die im Beispiel
gewählte Zahl) erfüllen die Gleichung und können damit zur Berechnung des
Sessionkeys benutzt werden: $285^{240}  \equiv 285^{67} \equiv 268 {\rm ~(mod~}347)$.
Hätten Alice und Bob als Basis $g$ eine Primitivwurzel\index{Primitivwurzel} modulo $p$ gewählt,
dann gibt es für jeden Rest aus der Menge
$\{1, 2, \cdots, p-1\}$ genau einen Exponenten aus der Menge $\{0, 1, \cdots, p-2\}.$ \\
Info: Zum Modul $347$ gibt es $172$ verschiedene Primitivwurzeln, davon sind $32$
prim (ist nicht notwendig).
Da die im Beispiel für $g$ gewählte Zahl $11$ keine Primitivwurzel\index{Primitivwurzel}
von $347$ ist, nehmen die Reste nicht alle Werte aus der Menge $\{1, 2, \cdots, 346\}$ an.
Somit kann es für einen bestimmten Rest mehr als einen oder auch gar keinen
Exponenten aus der Menge $\{0, 1, \cdots, 345\}$ geben, der die Gleichung
erfüllt. \\
Mit den entsprechenden Sage-Funktionen\index{Sage} findet man: \\
\texttt{is\_prime(347)=True}, \texttt{euler\_phi(347)=346}, \texttt{gcd(11,347)=1} und 
\texttt{multiplicative\_order(mod(11, 347))=173}.

### 2010-03-25 script/de/chapters/what-is-sage.tex
Minor grammar corrections in German and English script.

Wenn man eigene Funktionen entwickelt, sie ändert und aufruft, dann ist es viel einfacher,
die Entwicklung in einem eigenen Editor vorzunehmen, den Code als Sage-Skriptdatei zu
speichern und die Funktionen nicht-interaktiv auf der Kommandozeile auszuführen.
Beide Arten, Code zu entwickeln, wurde in den Beispielen in
Kapitel \ref{PaP_Sage_samples} (\glqq \nameref{PaP_Sage_samples}\grqq),
Kapitel \ref{Primes_Sage_samples} (\glqq \nameref{Primes_Sage_samples}\grqq)
und in Kapitel \ref{NumberTheory_Appendix_E} (\glqq\nameref{NumberTheory_Appendix_E}\grqq)
angewandt.

>>>>

Wenn man eigene Funktionen entwickelt, sie ändert und aufruft, dann ist es viel einfacher,
die Entwicklung in einem eigenen Editor vorzunehmen, den Code als Sage-Skriptdatei zu
speichern und die Funktionen nicht-interaktiv auf der Kommandozeile auszuführen.
Beide Arten, Code zu entwickeln, wurden in
Kapitel \ref{CM_Sage_samples} (\glqq \nameref{CM_Sage_samples}\grqq),
Kapitel \ref{PaP_Sage_samples} (\glqq \nameref{PaP_Sage_samples}\grqq),
Kapitel \ref{primes:_Appendix_Sage-Samples} (\glqq \nameref{primes:_Appendix_Sage-Samples}\grqq)
und in Kapitel \ref{NumberTheory_Appendix_E} (\glqq\nameref{NumberTheory_Appendix_E}\grqq)
angewandt.

### 2010-03-25 script/en/chapters/authors.tex
QA
Minor grammar corrections in German and English script.

\item[\textrm{[Seed1990]}] \index{Seed 1990}
    Directed by Paul Seed, \\
    {\em House of Cards}, 1990. \\
    In this movie Ruth tries to solve the secret, which made her daughter
    fall silent. Here two young people suffering from autism communicate
    via 5- and 6-digit primes (see 
    chapter~\ref{Label_Kapitel_2}).
    After more than 1 hour the movie contains the following encrypted
    two series of primes:
    \begin{center}
    $21,383; \;\;176,081; \;\;18,199; \;\;113,933; \;\;150,377; \;\;304,523; \;\;113,933$ \\
    $193,877; \;\;737,683; \;\;117,881; \;\;193,877$
    \end{center}
    % where autistic children communicate via primes
    \vskip +20 pt

@@

\paragraph{Remark 2:}
You can find title pages of some of these books on the web site of
Tobias Schr\"odel, who collects classic books about cryptography:
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

@@

\vskip +20 pt
\paragraph{Remark 1:}
You can find title pages of many of these kid books on the web site of
Tobias Schr\"odel, who collects classic books about cryptography:
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

>>>>

\item[\textrm{[Seed1990]}] \index{Seed 1990}
    Directed by Paul Seed, \\
    {\em House of Cards}, 1990. \\
    In this movie Ruth tries to solve the secret, which made her daughter
    fall silent. Here two young people suffering from autism communicate
    via 5- and 6-digit primes (see 
    chapter~\ref{Label_Kapitel_Primes}).
    After more than 1 hour the movie contains the following encrypted
    two series of primes:
    \begin{center}
    $21,383; \;\;176,081; \;\;18,199; \;\;113,933; \;\;150,377; \;\;304,523; \;\;113,933$ \\
    $193,877; \;\;737,683; \;\;117,881; \;\;193,877$
    \end{center}
    % where autistic children communicate via primes
    \vskip +20 pt

@@

\paragraph{Remark 2:}
You can find title pages of some of these books on the web site of
Tobias Schr\"odel\index{Schroedel, Tobias}, who collects classic books about cryptography:
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

@@

\vskip +20 pt
\paragraph{Remark 1:}
You can find title pages of many of these kid books on the web site of
Tobias Schr\"odel\index{Schroedel, Tobias}, who collects classic books about cryptography:
\parskip -4pt  % 1-BACK to DEFAULT -- Really necessary
\begin{center}
   \url{http://tobiasschroedel.com/crypto_books.php}
\end{center}
\parskip \value{mycounterDefaultParskip} pt  % 2-BACK to DEFAULT -- Really necessary
\vspace{1em}

### 2010-03-25 script/en/chapters/digitalsignatures.tex
Minor grammar corrections in German and English script.

Cryptographically secure hash functions fulfill the following three requirements
(the order is in a way that the requirements increase):
\begin{itemize}
 \item Resistance against 1st Pre-Image attacks:
      \index{Pre-Image-Attack!1st}  \\
      It should be practically impossible, for a given number, to find a
      message that has precisely this number as hash value. \\
      Given (fix): hash value H', \\
      Searched: message m, so that: H(m) = H'.
 \item Resistance against 2nd Pre-Image attacks:
      \index{Pre-Image-Attack!2nd}  \\
      It should be practically impossible, for a given message, to find another
      message, which has precisely the same hash value. \\
      Given (fix): message m1 [and so the hash value H1 = H(m1)], \\
      Searched: message m2, so that: H(m2) = H1.
 \item Collision resistance:
      \index{Collision resistance}  \\
      It should be practically impossible to find any two messages with the
      same hash value (it doesn't matter what hash value). \\
      Searched: 2 messages m1 and m2, so that: H(m1) = H(m2).
\end{itemize}

>>>>

Cryptographically secure hash functions fulfill the following three requirements
(the order is in a way that the requirements increase):
\begin{itemize}
 \item Resistance against 1st pre-image attacks:
      \index{Pre-image attack!1st} \index{Attack!pre-image!1st}   \\
      It should be practically impossible, for a given number, to find a
      message that has precisely this number as hash value. \\
      Given (fix): hash value H', \\
      Searched: message m, so that: H(m) = H'.
 \item Resistance against 2nd pre-image attacks:
      \index{Pre-image attack!2nd} \index{Attack!pre-image!2nd}   \\
      It should be practically impossible, for a given message, to find another
      message, which has precisely the same hash value. \\
      Given (fix): message m1 [and so the hash value H1 = H(m1)], \\
      Searched: message m2, so that: H(m2) = H1.
 \item Collision resistance:
      \index{Collision resistance}  \\
      It should be practically impossible to find any two messages with the
      same hash value (it doesn't matter what hash value). \\
      Searched: 2 messages m1 and m2, so that: H(m1) = H(m2).
\end{itemize}

### 2010-03-25 script/en/chapters/ellipticcurves.tex
Minor grammar corrections in German and English script.

CrypTool offers elliptic curves for the digital signature function%
\footnote{%
The dialog box, which appears in CrypTool\index{CrypTool} after clicking the menu
{\bf Digital Signatures/PKI \textbackslash{} Sign Message},
offers the EC methods ECSP-DSA and ECSP-NR.
} and for ECC-AES hybrid encryption%
\footnote{%
Within CrypTool\index{CrypTool} you can find this technique using the menu
path {\bf Crypt \textbackslash{} Hybrid}.

@@

Sage notebooks are running after a logon within a browser%
\footnote{%
If you installed Sage on your own (Unix) server, you first have to enter at the
command line the command \verb#notebook()#.
}${}^,$\footnote{%
The ECC notebook of Maike Massierer needs the KASH3 library: Therefore e.g.\ with Sage 4.2.1
the package ``kash3-2008-07-31.spkg'' has to be installed (command \verb#sage -i#).
}.

The ECC notebook\index{Elliptic curves!ECC notebook}\index{Massierer, Maike} of
Massierer\footnote{%
Instructions to use an interactive Sage noebook:\\

>>>>

CrypTool offers elliptic curves for the digital signature function%
\footnote{%
The dialog box, which appears in CrypTool\index{CrypTool} after clicking the menu
{\bf Digital Signatures/PKI \textbackslash{} Sign Message},
offers the EC methods ECSP-DSA and ECSP-NR.

} and for ECC-AES hybrid encryption%
\footnote{%
Within CrypTool\index{CrypTool} you can find this technique using the menu
path {\bf Crypt \textbackslash{} Hybrid}.

@@

Sage notebooks are running after a logon within a browser%
\footnote{%
If you installed Sage on your own (Unix) server, you first have to enter at the
command line the command \verb#notebook()#.

}${}^,$\footnote{%
The ECC notebook of Maike Massierer needs the KASH3 library: Therefore e.g.\ with Sage 4.2.1
the package ``kash3-2008-07-31.spkg'' has to be installed (command \verb#sage -i#).
}.

The ECC notebook\index{Elliptic curves!ECC notebook}\index{Massierer, Maike} of
Massierer\footnote{%
Instructions to use an interactive Sage notebook:\\

### 2010-03-25 script/en/chapters/moderncryptography.tex
Some more minor corrections in the script (German and English); Problem building English script.
Minor grammar corrections in German and English script.

To this date, it has not been proved that the problem of breaking RSA is 
equivalent to the factorization problem. Nevertheless, it is clear that
the RSA procedure will no longer be safe if the factorization problem is
``solved''.\footnote{%
In 2000 the authors assumed that values of the order magnitude $ 100 $ to $ 200 $
decimal places are currently safe. They estimates that the current computer
technology indicates that a number with $100$ decimal places could be
factorized in approximately two weeks at justifiable costs, and using an 
expensive configuration (e.g. of around 10 million US dollars), a number with 
$150$ decimal places could be factorized in about a year, and a $200$-digit
number should remain impossible to factorize for a long time to come, unless
there is a mathematical breakthrough. However, you can never be sure that
there won't be a mathematical breakthrough tomorrow.\\
How easy it is to guess the future wrong is shown by the
\hyperlink{RSA-200-chap3}{Factorization of RSA-200} 
(see chapter \ref{NoteFactorization}) -- completely without a
``mathematical breakthrough''.}

@@

\noindent \hyperlink{ellcurve}{Elliptic curves} {} provide useful groups for public key 
encryption procedures.

>>>>

To this date, it has not been proved that the problem of breaking RSA is 
equivalent to the factorization problem. Nevertheless, it is clear that
the RSA procedure will no longer be safe if the factorization problem is
``solved''.\footnote{%
In 2000 the authors assumed that values of the order magnitude $ 100 $ to $ 200 $
decimal places are currently safe. They estimates that the current computer
technology indicates that a number with $100$ decimal places could be
factorized in approximately two weeks at justifiable costs, and using an 
expensive configuration (e.g. of around 10 million US dollars), a number with 
$150$ decimal places could be factorized in about a year, and a $200$-digit
number should remain impossible to factorize for a long time to come, unless
there is a mathematical breakthrough. However, you can never be sure that
there won't be a mathematical breakthrough tomorrow.\\
How easy it is to guess the future wrong is shown by the
\hyperlink{RSA-200-chap3}{factorization of RSA-200} 
(see chapter \ref{nt:NoteFactorization}) -- completely without a
``mathematical breakthrough''.}

@@

\noindent \hyperlink{ellcurve}{Elliptic curves}{} provide useful groups for public key 
encryption procedures.

### 2010-03-25 script/en/chapters/numbertheory.tex
fixed overfull \hbox and undefined references
Minor grammar corrections in German and English script.

\noindent Current research results on this topic can be found at:
\vspace{-10pt}
\begin{itemize}
  \item[] \url{http://www.mersenne.org/} \\
          \url{http://fatphil.org/maths/AKS/} Original paper in English\\
          \url{http://ls2-www.cs.uni-dortmund.de/lehre/winter200203/kt/material/primes.ps} \\
	  \hspace*{2em}Good explanation in German by Thomas Hofmeister.
\end{itemize}
\vskip +10 pt

@@

\noindent b) Calling \verb#sage: count_Number_of_RSA_Keys(100, 100, True)# has the following output:\\
   - Number of private keys for modulus in a given range: 0\\
   - Number of primes in a given range: 0\\
   The reason for that is, that now we only consider $n=100$, and $100$ is not
   semi-prime\index{Prime number!semi-prime}\index{Prime number!half prime}\index{Half prime},
   this means $100$ is not the product of only two primes.
}

>>>>

\noindent Current research results on this topic can be found at:
\vspace{-10pt}
\begin{itemize}
  \item[] \url{http://www.mersenne.org/} \\
          \url{http://fatphil.org/maths/AKS/} Original paper in English\\
          \href{http://ls2-www.cs.uni-dortmund.de/lehre/winter200203/kt/material/primes.ps}{\tt http://ls2-www.cs.uni-dortmund.de/lehre/winter200203/kt/material/primes.ps} \\% \url... created overfull \hbox
	  \hspace*{2em}Good explanation in German by Thomas Hofmeister.
\end{itemize}
\vskip +10 pt

@@

\noindent b) Calling \verb#sage: count_Number_of_RSA_Keys(100, 100, True)# has the following output:\\
   - Number of private keys for modulus in a given range: 0\\
   - Number of primes in a given range: 0\\
   The reason for that is, that now we only consider $n=100$, and $100$ is not
   semi prime\index{Prime number!semi prime}\index{Prime number!half prime}\index{Half prime},
   this means $100$ is not the product of only two primes.
}

### 2010-03-25 script/en/chapters/what-is-sage.tex
Minor grammar corrections in German and English script.

But if you develop your own functions, modify them and call them, then it is much easier
to do the development in your own editor, save it to a script file and execute the functions
non-interactively on the command line manually.
Both ways to develop code is done in the examples in
chapter \ref{PaP_Sage_samples} (``\nameref{PaP_Sage_samples}''), 
chapter \ref{Primes_Sage_samples} (``\nameref{Primes_Sage_samples}'') and in
chapter \ref{NumberTheory_Appendix_E} (``\nameref{NumberTheory_Appendix_E}'').

>>>>

But if you develop your own functions, modify them and call them, then it is much easier
to do the development in your own editor, save it to a script file and execute the functions
non-interactively on the command line manually.
Both ways to develop code were applied in
chapter \ref{CM_Sage_samples} (``\nameref{CM_Sage_samples}''), 
chapter \ref{PaP_Sage_samples} (``\nameref{PaP_Sage_samples}''), 
chapter \ref{primes:_Appendix_Sage-Samples} (``\nameref{primes:_Appendix_Sage-Samples}'') and in
chapter \ref{NumberTheory_Appendix_E} (``\nameref{NumberTheory_Appendix_E}'').
